Communicating with convexity

### 2017-12-01 article_cvxpy.tex
minor edits to python version, waterfilling and sigma

\subsection{Disciplined convex programming}
\noindent In order to solve convex optimisation problems, we used \texttt{cvxpy}, a symbolic programming module for Python \cite{cvxpy} (all example code is given for Python $3.0$). It uses a set of rules, called \textit{disciplined convex programming} (DCP), to determine whether a function is convex. This is implemented using predefined classes containing functions with their curvature and sign, and using general composition theorems from convex analysis \cite{dcp}. If DCP rules can be applied then interior point methods guarantee an optimal solution. 
%Interior point methods work by applying Newton's algorithm to sequences of equally constrained problems. Is it right that Newton's method is used???
 The algorithm works by picking a step and direction to travel in the interior of the feasible convex set, such that the solution progresses towards optimality. For more details on barrier methods and primal-dual methods see \citep[p.561]{cvxpybook}.

@@

\subsection{Implementation}
\noindent We decided to solve the water-filling problem using \texttt{cvxpy} with $n=3$ channels and $(\alpha_1,\alpha_2,\alpha_3) = (0.8,1.0,1.2)$.  For simplicity we chose a dimensionless total power $P=1$.  Using these parameters, the maximum communication rate is, $\sum_{i=1}^{n}r_i = 0.863$, which is achieved with power allocations $(x_1,x_2,x_3) = (8/15,5/15,2/15)$.  This solution is shown in Figure~\ref{fig:waterfilling}, and can be seen as being analogous to filling an uneven basin to a constant level (hence the name \textit{water-filling}).

\subsection{Example Code}
\noindent To indicate the brevity of code implementation in \texttt{cvxpy} we show a minimal working example below with the parameters chosen above.  With an ordinary commercially available laptop, the time taken to execute the code was around 4ms. Note that the code is a little different in formulation from the text in that it maximises the positive sum of $x_i$ rather than minimising the negative. The total power constraint is also rearranged.
\lstinputlisting[language=Python,mathescape=true,inputencoding=utf8,literate={α}{$\alpha$}1 ]{waterfilling.py}

@@

How can we minimise the total power consumption, $P$, of the transmitters, yet achieve this minimum SINR, $\gamma_0$, for all $i$ receivers ($i = 1,2,...,m$)? This question is relevant to telecom companies who want to offer a service at a minimum quality standard. We formulate the problem with a given square path-gain matrix, $G$, background noise level vector, $\sigma$, a maximum power constraint, $P_{\text{max}}$, of each transmitter and the fact that all transmitters must be supplied with positive power:
\begin{align*}
&\underset{p}{\text{minimise}} \quad &&\sum_k p_k\\
&\text{subject to} \quad &&p_k \leqslant P_{\max}\\
& \quad &&p_k \geqslant 0\\
& \quad &&\gamma_i \geqslant \gamma_0.&&
\end{align*}

@@

All the parameters we will take as dimensionless to give simple numbers to work with.  The maximum available power, $P_{\text{max}}$ is set to 1.  We have chosen the background noise vector $\sigma$ as constant for each receiver, with $\sigma_i = 5$.  Similarly, the receiver coefficient $A$ was set to $0.025$ for each receiver. \\

>>>>

\subsection{Disciplined convex programming}
\noindent In order to solve convex optimisation problems, we used \texttt{cvxpy}, a symbolic programming module for Python \cite{cvxpy} (all example code is given for Python 3). It uses a set of rules, called \textit{disciplined convex programming} (DCP), to determine whether a function is convex. This is implemented using predefined classes containing functions with their curvature and sign, and using general composition theorems from convex analysis \cite{dcp}. If DCP rules can be applied then interior point methods guarantee an optimal solution. 
%Interior point methods work by applying Newton's algorithm to sequences of equally constrained problems. Is it right that Newton's method is used???
 The algorithm works by picking a step and direction to travel in the interior of the feasible convex set, such that the solution progresses towards optimality. For more details on barrier methods and primal-dual methods see \citep[p.561]{cvxpybook}.

@@

\subsection{Implementation}
\noindent We decided to solve the water-filling problem using \texttt{cvxpy} with $n=3$ channels and $(\alpha_1,\alpha_2,\alpha_3) = (4/5,1,6/5)$.  For simplicity we chose a dimensionless total power $P=1$.  Using these parameters, the maximum communication rate is, $\sum_{i=1}^{n}r_i = 0.863$, which is achieved with power allocations $(x_1,x_2,x_3) = (8/15,5/15,2/15)$.  This solution is shown in Figure~\ref{fig:waterfilling}, and can be seen as being analogous to filling an uneven basin to a constant level (hence the name \textit{water-filling}).

\subsection{Example Code}
\noindent To indicate the brevity of code implementation in \texttt{cvxpy} we show a minimal working example below with the parameters chosen above.  With an ordinary commercially available laptop, the time taken to execute the code was around 4ms. Note that the code is a little different in formulation from the text in that it maximises $\sum_{i}^nr_i$ rather than minimising $\sum_{i}^{n}-r_i$. The total power constraint is also rearranged to: $\sum_i^nx_i - P = 0$.
\lstinputlisting[language=Python,mathescape=true,inputencoding=utf8,literate={α}{$\alpha$}1 ]{waterfilling.py}

@@

How can we minimise the total power consumption, $P$, of the transmitters, yet achieve this minimum SINR, $\gamma_0$, for all $i$ receivers ($i = 1,2,...,m$)? This question is relevant to telecom companies who want to offer a service at a minimum quality standard. We formulate the problem with a given square path-gain matrix, $G$, background noise level vector, $\boldsymbol{\sigma} = (\sigma_1, \sigma_2, ..., \sigma_i, ..., \sigma_m)$, a maximum power constraint, $P_{\text{max}}$, of each transmitter and the fact that all transmitters must be supplied with positive power:
\begin{align*}
&\underset{p}{\text{minimise}} \quad &&\sum_k p_k\\
&\text{subject to} \quad &&p_k \leqslant P_{\max}\\
& \quad &&p_k \geqslant 0\\
& \quad &&\gamma_i \geqslant \gamma_0.&&
\end{align*}

@@

All the parameters we will take as dimensionless to give simple numbers to work with.  The maximum available power, $P_{\text{max}}$ is set to 1.  We have chosen the background noise vector $\boldsymbol{\sigma}$ as constant for each receiver, with $\sigma_i = 5$.  Similarly, the receiver coefficient $A$ was set to $0.025$ for each receiver. \\
